---
title: "Exercise 1"
author: "Helene"
date: "22/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(scales)

```




## Create Data
First, we need to generate a random sample from a log-normal distribution with $\mu= 1$ and $\sigma=0.25$. 

```{r}
set.seed(323883501)

n <- 100
mu <- 1
sigma <- 0.25

data1 <- rlnorm(n, mu, sigma)
```

Using the rlnorm- command without adjusting leads to a dataset with mean `r round(mean(data1),4)` and standard deviation `r round(sd(data1), 4)`.

We could reparameterize such that the mean would be 1 and the standard deviation 0.25, but I think that's not needed here (unless I misinterpreted the task).


## Plots
### Normal Histogram
To plot a histogram, we use ggplot. To do this we prepare the data (I don't really know if this is necessary, but it works)

```{r}
useddata <-data.frame(data1)

```

and set the binwidth to 0.1 so that the plot doesn't become too confusing

```{r}
plot <- ggplot(useddata, aes(x = data1), y= count)+ geom_histogram(binwidth = 0.1) 
plot

```

### Logscale Density

to plot the density on a logscale, we also use ggplot

```{r}
dense <- ggplot(useddata, aes(x = data1)) + geom_density() + scale_x_log10()
dense
```


I hope this is what you expected from the task. I am pretty sure that there are way more elegant and straight-forward ways to do it. Nevertheless I would like to ask you to be mild, because I never did anything with R before. 



